Size-differentiated Export in different Dynamical Regimes in the Ocean

### 2019-06-11 size_differentiated_export.tex

%FIG6
\begin{figure}[ht]
	\centering
	\includegraphics[width = 1\linewidth]{figures/Fig6_particle_export_flux.png}
	\caption{Upward (top) and downward (bottom) fluxes of particles (thin lines) at the 100 m depth horizon as a function of time in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right). Fluxes are normalized by the total amount of particles (N = 1,971,717), daily-averaged and integrated over the entire domain. For each sinking-velocity class, the net particle flux is shown by a thick line. Expected downward fluxes based on only gravitational sinking are indicated with dashed lines in the left panels.}
	\label{fig: particle_export}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width = 1\linewidth]{figures/Fig6b_biomass_export_flux.png}
	\caption{Net biomass flux in normalized units in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for two different Junge slopes: $\xi =$ 4 (solid lines) and $\xi =$ 2 (dashed lines; see Figure \ref{fig: sinking_velocity_spectrum}). Biomass export flux for the 5 m/day sinking-velocity class remains unchanged, as it is used as a reference class in Equation (\ref{eq: biomassjungeslope}) ($w_{s_0} = 5$ m/day).}
	\label{fig: biomass_export}
\end{figure}

@@

 %FIG7
 \begin{figure}[t]
	\centering
	\includegraphics[width = 1\linewidth]{figures/Fig7_biomass_export_flux_remin.png}
	\caption{Net biomass flux in normalized units in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for $\xi=4$. Dashed lines represent the case without remineralization, while solid lines include the remineralization scheme described in Section \ref{sec: remin_scheme}.}
	\label{fig: biomass_export_remin}
\end{figure}

>>>>

%FIG6
\begin{figure}[ht]
	\centering
	%\includegraphics[width = 1\linewidth]{figures/Fig6_particle_export_flux.png}
	%\caption{Upward (top) and downward (bottom) fluxes of particles (thin lines) at the 100 m depth horizon as a function of time in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right). Fluxes are normalized by the total amount of particles (N = 1,971,717), daily-averaged and integrated over the entire domain. For each sinking-velocity class, the net particle flux is shown by a thick line. Expected downward fluxes based on only gravitational sinking are indicated with dashed lines in the left panels.}
	\includegraphics[width = 1\linewidth]{figures/Fig6.png}
	\caption{[left] Gridded depth anomaly in the median particle depth 25 days after particle release, in the Winter experiment. Blue (red) grid cells indicate that the median depth of particles in this cell is deeper (shallower) than expected based on a 1D gravitational model. [right]  Depth profile of the PDF of the number of particle for each velocity class. The winter distribution is shown as thick lines, while the summer distribution is represented by the shaded regions. Triangle markers indicate the expected depth of particles after 25 days based on the 1D gravitational model, which is used as a reference to compute the depth anomalies. Release depth is indicated by the thick dashed line.}	
	\label{fig: particle_export}
\end{figure}

@@

\begin{figure}[t]
	\centering
	%\includegraphics[width = 1\linewidth]{figures/Fig6b_biomass_export_flux.png}
	%\caption{Net biomass flux in normalized units in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for two different Junge slopes: $\xi =$ 4 (solid lines) and $\xi =$ 2 (dashed lines; see Figure \ref{fig: sinking_velocity_spectrum}). Biomass export flux for the 5 m/day sinking-velocity class remains unchanged, as it is used as a reference class in Equation (\ref{eq: biomassjungeslope}) ($w_{s_0} = 5$ m/day).}
	\includegraphics[width = 1\linewidth]{figures/Fig7.png}
	\caption{PDF of biomass versus vertical velocity along particle trajectories in the summer case [left] and winter case [right], with a Junge slope of 2 [top] and 4 [bottom]. Inserts show the total downward biomass flux associated with each sinking-velocity class. Both winter dynamics and steeper June slope tend to increase the relative contribution of slower-sinking particles.}	
	\label{fig: biomass_export}
\end{figure}

@@

 %FIG7
 \begin{figure}[t]
	\centering
	%\includegraphics[width = 1\linewidth]{figures/Fig7_biomass_export_flux_remin.png}
	%\caption{Net biomass flux in normalized units in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for $\xi=4$. Dashed lines represent the case without remineralization, while solid lines include the remineralization scheme described in Section \ref{sec: remin_scheme}.}
	\includegraphics[width = 1\linewidth]{figures/Fig8.png}
	\caption{Snapshot of the biomass PDF versus vertical velocity along particle trajectories in the summer case [left] and winter case [right], ignoring [top] and including [bottom] particle remineralization, for $\xi$ = 4 and 25 days after particle release. Inserts show the total downward biomass flux associated with each sinking-velocity class. Remineralization processes have the greatest impact on fast-sinking particles, especially in summer dynamics.}	
	\label{fig: biomass_export_remin}
\end{figure}
